---
title: "FInal-Project"
author: "Paul Wu"
date: "4/3/2019"
output: html_document
---

1. importing data (Original Dataset)
```{r}
library(ggplot2)
load("36828-0005-Data.rda")
head(da36828.0005, 5) ## first 5 rows of the original dataset
paste("Number of rows of the original dataset: ", nrow(da36828.0005)) ## number of rows of the original dataset
paste("number of variables of the original dataset: ", ncol(da36828.0005)) ## number of variables of the original dataset
length(da36828.0005$INCREPWGT158)

```

2. Adjusted dataset
```{r}
library(dplyr)
data = select(da36828.0005,IDHH,V2113,V2024,V2025A,V2026, V2071, V2072, V2074, V2078,V2119,V2125,V2127B,V2116,WGTHHCY) ## Adjust dataset

head(data, 5) ## first 5 rows of the Adjust dataset
paste("Number of rows of the Adjust dataset: ", nrow(data)) ## number of rows of the Adjusted dataset
paste("number of variables of the Adjust dataset: ", ncol(data)) ## number of variables of the Adjusted dataset

```

3. clean data
```{r}
##change column names
colnames(data)[1] <- "HH.ID" #household ID in the survey
colnames(data)[2] <- "num.in" ##number of incidents recorded
colnames(data)[3] <- "num.unit" ##number of housing units in the address
colnames(data)[4] <- "g.or.w" ##gated or walled community
colnames(data)[5] <- "hh.income" ##household income
colnames(data)[6] <- "num.age>12" ##number of memebers aged 12 and above
colnames(data)[7] <- "num.age<12"##number of members aged 12 and younger
colnames(data)[8] <- "oper.bus"##operate business from address
colnames(data)[9] <- "num.car" ##number of cars owned
colnames(data)[10] <- "college?" ##education level of victim 
colnames(data)[11] <- "land.use" ##urban or rural
colnames(data)[12] <- "hh.region" ##region of the household
colnames(data)[13] <- "hh.weight" ##household weight
colnames(data)[14] <- "WGTHHCY" ##adjusted household weight
head(data)

##adjusting the categorical data
data <- data %>%
  mutate(g.or.w = ifelse(g.or.w == "(2) No", 0, 1))#g.or.w

data<-data[!duplicated(data$HH.ID), ]
```

4. select variables, using AIC selection
```{r}
data1 = data[,c(2,6,7)]
lm.fit = lm(num.in~., data1)
step(lm.fit, direction = "both", k = 2, trace = FALSE)
summary(lm(data$num.in~data$`num.age>12`+data$`num.age<12`))


data1 = data[,c(2,3,4,5,8,9,10,11,12)]
lm.fit = lm(num.in~., data1)
step(lm.fit, direction = "both", k = 2, trace = FALSE)
summary(lm(data$num.in~data$num.unit+data$g.or.w+data$hh.income+data$oper.bus+data$num.car+data$`college?`+data$land.use+data$hh.region))
```

5. # of incidents and region
```{r}
summary(data$num.in)
summary(data$hh.region)

## # of total incidents of each region 
data1 = data.frame(
"Northeast" = sum(filter(data[ ,c(2,12)], hh.region == "(1) Northeast")[,1]),
"Midwest" = sum(filter(data[ ,c(2,12)], hh.region == "(2) Midwest")[,1]),
"South" = sum(filter(data[ ,c(2,12)], hh.region == "(3) South")[,1]),
"West" = sum(filter(data[ ,c(2,12)], hh.region == "(4) West")[,1]))

data_region = data[,c(2,12)]

## Then the null hypothesis is that "the people who live in the South side of America surferred the crime most."
```

Remove NA; 7. # of incidents and Income
```{r}
data_income = data[, c(2,5)]
summary(lm(data$num.in~data$hh.income))

model.matrix(~num.in+hh.income, data=data)

N = nrow(data)
srsMiss_design<-svydesign(id=~1, fpc=rep(N,nrow(data_income)),data=data_income)
srsNoNA_design<-subset(srsMiss_design, acresMissing!=1)
```
6. Chi-square test (Result: it is independent)
```{r}
library(survey)
data_region =  xtabs(~num.in+hh.region,data = data)

chisq.test(data_region)

```

7. # of incidents and Income (dependent, positive relationship)
```{r}
summary(lm(data$num.in~data$hh.income))

plot(data$num.in~data$hh.income)

data_income =  xtabs(~num.in+hh.income,data = data)


data_income = data.frame(data_income)

data_income_1 = filter(data_income, data_income$num.in == 1)
plot(data_income_1$Freq~data_income_1$hh.income)
abline(lm(data_income_1$Freq~data_income_1$hh.income))


barplot(x = data_income_1[,2], y = data_income_1[,3])


ggplot(data_income, aes(data_income[,2], data_income[,3])) +
  xlab("Income Intervals") + 
  ylab("# of Household has 1 Incident") +
  geom_col(aes(fill = hh.income)) 
  

```

8. # of incidents and Age >12
```{r}
## Age > 12
data_AgeLarger12 = data[,c(2,6)]
summary(lm(data_AgeLarger12$num.in~data_AgeLarger12$`num.age>12`))

#Chi square test
tbl3<-xtabs(~num.in + data$`num.age>12`, data=data)
chisq.test(tbl3)

#geom plot
ggplot(data, aes(x=`num.age>12`,y=num.in)) +
  geom_point(aes( color=`num.age>12`)) + 
  xlab("Number of People Aged > 12") +
  ylab("Number of Incidents")
```

8. # Age of < 12
```{r}
library(dplyr)
## Age < 12
data_AgeLarger12 = data[,c(2,6)]
summary(lm(data_AgeLarger12$num.in~data_AgeLarger12$`num.age>12`))

#Chi square test
tbl4<-xtabs(~num.in + data$`num.age<12`, data=data)
chisq.test(tbl4)

#geom plot
ggplot(data, aes(x=`num.age<12`,y=num.in))+geom_point(aes(color=num.in))+geom_smooth(method = lm, color="Red")+xlab("Number of People Aged < 12")+ylab("Number of Incidents")

group_by(data,`num.age>12`)%>%
  summarise(
    count=n(),
    mean = mean(num.in),
    sd = sd(num.in)
  )

boxplot(num.in~data$`num.age<12`,data = data)
boxplot(num.in~data$`num.age>12`,data = data)

```

9. # car  (byebye not considered anymore)
```{r}
data_car = data[,c(2,9)]
summary(lm(data_car$num.in~data_car$num.car))
filter(data_car, data_car$num.car!="(8) Residue")
plot(data_car$num.car,data_car$num.in)
tbls4<-xtabs(~num.car+hh.income, data = data)
chisq.test(tbl4)

ggplot(data, aes(x=num.car,y=num.in)) +
  geom_col(aes( color=num.car)) + 
  xlab("Number of People Aged > 12") +
  ylab("Number of Incidents")+geom_line()
```

```{r}
a = data.frame(group = "Unadjusted.HH", value = da36828.0005$V2116)
b = data.frame(group = "Adjusted.HH", value = da36828.0005$WGTHHCY)
plot.data = rbind(a,b)
ggplot(plot.data, aes(x=group,y=value,fill=group))+geom_boxplot()

c = data.frame(group = "Unadjusted.PP", value = da36828.0005$V3080)
d = data.frame(group = "Adjusted.PP", value = da36828.0005$WGTPERCY)
plot.data = rbind(c,d)
ggplot(plot.data, aes(x=group,y=value,fill=group))+geom_boxplot()+scale_y_continuous(name="Stopping distance", breaks = seq(0,200000,2000))

e = data.frame(group = "Unadjusted.In", value = da36828.0005$)
f = data.frame(group = "Adjusted.In", value = da36828.0005$SERIES_IWEIGHT)
plot.data = rbind(c,d)
ggplot(plot.data, aes(x=group,y=value,fill=group))+geom_boxplot()+scale_y_continuous(name="Stopping distance", breaks = seq(0,200000,2000))
```
